A method for defining dispersed community territories

### 2024-03-04 manuscript/manuscript.qmd
minor edits

Our clustering algorithm draws inspiration from the procedure used by the United
States Office of Management and Budget to define Core Based Statistical Areas
(CBSA) [@usomb2021]. We start by defining a core area, in this case a community
center location. We then merge core areas into larger agglomerations based on
the proportion of their populations that they share. Our method may be described
as a guided density-based clustering algorithm in that it does not rely on a
random set of points when initialized. Instead, the selection of core areas is
guided by archaeological data and regional expertise. We think this is a key
argument in its favor.

@@

Archaeologists and anthropologists have investigated various dimensions of
community organization and the types of communities they foster. Examples
include biological communities organized around genetic relatedness or physical
similarities [@becker_juengst2017; @kakaliouras2017; @blom2005; @blom2017],
imagined or ideational communities organized around perceived membership and
metaphors [sometimes called *styles of imaginings;* @ortman2011; @anderson1983;
@isbell2000], reproductive communities organized around mating opportunities
[@mahoney_etal2000; @kolb_snead1997], religious communities organized around a
shared sense of the sacred [@bernardini2004; @malville_malville2001], linguistic
communities organized around a shared grammar and vocabulary [@gumperz1968;
@silverstein1998], even sight communities organized around a shared set of
visually striking landmarks [@bernardini_peeples2015]. In fact, there are
probably as many types of communities as there are types of things for people to
care about.

>>>>

Our clustering algorithm draws inspiration from the procedure used by the United
States Office of Management and Budget to define Core Based Statistical Areas
(CBSA) [@usomb2021]. We start by defining a core area, in this case a community
center location. We then associate outlying areas with their nearest core area
and merge core areas into larger agglomerations based on the proportion of their
populations that they share. Our method may be described as a guided
density-based clustering algorithm in that it does not rely on a random set of
points when initialized. Instead, the selection of core areas is guided by
archaeological data and regional expertise. We think this is a key argument in
its favor.

@@

Archaeologists and anthropologists have investigated various dimensions of
community organization and the types of communities they foster. Examples
include biological communities organized around genetic relatedness or physical
similarities [@becker_juengst2017; @kakaliouras2017; @blom2005; @blom2017],
imagined or ideational communities organized around perceived membership and
metaphors [sometimes called *styles of imaginings;* @anderson1983; @ortman2011;
@isbell2000], reproductive communities organized around mating opportunities
[@mahoney_etal2000; @kolb_snead1997], religious communities organized around a
shared sense of the sacred [@bernardini2004; @malville_malville2001], linguistic
communities organized around a shared grammar and vocabulary [@gumperz1968;
@silverstein1998], even sight communities organized around a shared set of
visually striking landmarks [@bernardini_peeples2015]. In fact, there are
probably as many types of communities as there are types of things for people to
care about.
